---
title: "Data Exploration - Portfolio"
author: "Johannes Bubeck"
date: "21.10.2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Libraries
```{r library, message=FALSE, warning=FALSE, paged.print=FALSE}
library("tidyverse")
library("igraph") 
library("tidygraph") 
library("ggraph")
library("ggplot2")
```


## Import Dataset 
```{r import, message=FALSE, warning=FALSE, paged.print=FALSE}
dat <- read_csv('Data/reachability-meta.csv')
dat2 <- read.table('Data/reachability.txt')
```

## Renaming Columns
```{r}
dat2 <- dat2 %>% 
  rename(
    from = V1,
    weight = V2,
    to = V3
  )
```


## Exploring Dataset
This is a transportation reachability network for cities in the United States and Canada. Edges are weighted so that there is an edge from city i to city j if the estimated airline travel time is less than a threshold. The travel time includes estimated stopover delays. Due to headwinds, the network is asymmetric. We include the city metropolitan populations, latitude, and longitude in this dataset.
```{r exploring dat}
head(dat)
summary(dat)
```

```{r exploring dat2}
head(dat2)
summary(dat2)
```


## First Plots
```{r first plots}
net <- as_tbl_graph(dat2)

# plot(net)

ggraph(net) +
  geom_node_point() +
  geom_edge_link(alpha = 0.3)

```

## Visualisierungen
```{r viz}
degree <- degree(net)

degree_df <- as.data.frame(degree)


ggplot(data = degree_df, aes(x = degree)) +
  geom_bar(size = .8) +
  theme_classic() +
  scale_y_log10()

```


## Erste Fragestellungen
1. Werden Flughäfen in Städten, in denen mehr Einwohner wohnen, häufiger angeflogen?
2. 

